---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# thresholdr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/thresholdr)](https://CRAN.R-project.org/package=thresholdr)
[![R-CMD-check](https://github.com/r-dcm/thresholdr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-dcm/thresholdr/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-dcm/thresholdr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-dcm/thresholdr?branch=main)
<!-- badges: end -->

The goal of thresholdr is to estimate optimal probability thresholds for determining classifications when the true state is unknown, such as when using diagnostic classification models.

## Installation

You can install the development version of thresholdr like so:

``` r
# install.packages("remotes")
remotes::install_github("r-dcm/thresholdr")
```

## Example usage

There the true classifications are known, we can determine the optimal threshold using a supported method, such as Youden's J statistic.
For example, using simulated data where the true attribute classifications are known, we can calculate the optimal probability classification threshold using `calc_youden()`:

```{r example}
library(thresholdr)

calc_youden(estimates = dcm_probs$att1$estimate,
            truth = dcm_probs$att1$truth)
```

However, in practice the true attribute classifications are unknown. In this scenario, we can estimate what the optimal threshold should be using, for example, resampling:

```{r}
optimal_resample(estimates = dcm_probs$att1$estimate, optimal_method = "youden")
```

This results in a threshold that is similar, although slightly higher, than what we know the true optimal threshold should be.
We can also visualize our estimate on an ROC curve.
Here again we see that our estimated optimal threshold from the resamples are very close to the true value.

```{r echo = FALSE}
library(tidyverse)
library(posterior)

yd_op <- calc_youden(estimates = dcm_probs$att1$estimate,
                     truth = dcm_probs$att1$truth)
yd_rs <- optimal_resample(estimates = dcm_probs$att1$estimate,
                          optimal_method = "youden")

create_roc(estimates = dcm_probs$att1$estimate,
           truth = dcm_probs$att1$truth) |> 
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path() +
  geom_point(data = ~filter(.x, .threshold == yd_op),
             aes(x = 1 - specificity, y = sensitivity,
                 color = "Youden's J")) +
  geom_point(data = yd_rs,
             aes(x = 1 - E(specificity), y = E(sensitivity),
                 color = "Resample Estimate")) +
  geom_abline(lty = 3) +
  coord_equal() +
  theme_bw()
```

